SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-09-13 MDPI/sensors-1915564/template.tex
Update Review 1.5

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of \add[H.K.D]{one} SOTA model \change[H.K.D]{such as}{including} DenseNet, InceptionNet, ResNet, NasNet,  MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth to note that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.989, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & AUC(AD) & AUC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.971 & \textbf{0.975}\\
		\hline
		DenseNet201 & 0.93 & \textbf{0.97}\\
		\hline
		ResNet50 & \textbf{0.95} & 0.93 \\
		\hline
		ResNet152 & 0.97 & 0.87\\
		\hline
		NasNetLarge & - & \textbf{0.96}\\
		\hline
		MobileNetV2 & 0.95 & \textbf{0.97}\\
		\hline
		MobileNetV3Small & 0.67 & \textbf{0.96}\\
		\hline
		MobileNetV3Large & 0.96 & \textbf{0.97}\\
		\hline
		NasNetMobile & 0.96 & \textbf{0.97}\\
		\hline
	\end{tabular}
	\caption{AUC (area under the curve) of all models. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-auc}
\end{table}

\begin{figure}[!htb]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{Definitions/ROC/densenet201}
		\caption{DenseNet201 Class ROC}\label{fig:densenet201auc}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{Definitions/ROC/irv2}
		\caption{InceptionResNetV2 Class ROC}\label{fig:irv2auc}
	\end{minipage}
\end{figure}

@@

After reviewing, the InceptionResNetV2 is found to be the best model trained. Futhermore, the InceptionResNetV2 is compared with the other state of the art researched model. According to the Table \ref{table:comparative-analysis}, there are six research that use the same data set: HAM10000 but different approaches. These models used in that research are also SOTA models sorted in ascending order. The Table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively. However, since Soumyyak et al use data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower. This is because the model in that research can only classify well on NV and VASC class which have the highest number of samples. On the other hand, the InceptionResNetV2 in this research also outperform the other model according to 5 indicator: accuracy, precision, f1-score, recall score, and auc score. 
\FloatBarrier
\begin{table}[H]
	\centering
	\begin{tabular}{| p{4cm} | c | c | c | c | c |}
		\hline
		Model & Accuracy & Precision & f1-score & recall & auc-score\\
		\hline
		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & 0.975\\
		\hline
		InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & 0.97\\
		\hline
		\cite{03798} & - & 0.88 & 0.77 & 0.74 & - \\
		\hline
		\cite{09418} & 0.88 & - & - & - & - \\
		\hline
		\cite{01284} & 0.86 & - & - & - & - \\
		\hline
		GradCam and Kernel SHAP\cite{06612} & 0.88 & - & - & - & - \\
		\hline
		Student and Teacher\cite{03225} & 0.85 & 0.76 & 0.76 & - & - \\
		\hline
	\end{tabular}
	\caption{Comparative Analysis}
	\label{table:comparative-analysis}
\end{table}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of \add[H.K.D]{one} SOTA model \change[H.K.D]{such as}{including} DenseNet, InceptionNet, ResNet, NasNet,  MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth to note that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c  c | }
		\hline
		Model & AUC(AD) & AUC(MD)\\ 
		\hline
		InceptionResNetV2 & 0.971 & \textbf{0.99}\\
		\hline
		DenseNet201 & 0.93 & \textbf{0.99}\\
		\hline
		ResNet50 & \textbf{0.95} & 0.93 \\
		\hline
		ResNet152 & 0.97 & 0.87\\
		\hline
		NasNetLarge & - & \textbf{0.96}\\
		\hline
		MobileNetV2 & 0.95 & \textbf{0.97}\\
		\hline
		MobileNetV3Small & 0.67 & \textbf{0.96}\\
		\hline
		MobileNetV3Large & 0.96 & \textbf{0.97}\\
		\hline
		NasNetMobile & 0.96 & \textbf{0.97}\\
		\hline
	\end{tabular}
	\caption{AUC (area under the curve) of all models. AD stands for augmented data, this indicate that the model is trained with augmented data. MD stands for Metadata which indicate that the model is trained with Metadata}
	\label{table:overall-auc}
\end{table}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/ROC/denvsirv2}
	\caption{ROC of DenseNet201 and InceptionResNetV2}\label{fig:densenet201auc}
\end{figure}

@@

After reviewing, the InceptionResNetV2 is found to be the best model trained. Futhermore, the InceptionResNetV2 is compared with the other state of the art researched model. According to the Table \ref{table:comparative-analysis}, there are six research that use the same data set: HAM10000 but different approaches. These models used in that research are also SOTA models sorted in ascending order. The Table shows that the accuracy of the combination of InceptionResNetV2 with Soft-Attention, metadata and weight loss in this research is less than the InceptionResNetV2 with Soft-Attention and augmented data: 0.90 compared to 0.93 respectively. However, since Soumyyak et al use data augmentation for all class of an imbalanced data set, the f1-score and recall score are much lower. This is because the model in that research can only classify well on NV and VASC class which have the highest number of samples. On the other hand, the InceptionResNetV2 in this research also outperform the other model according to 5 indicator: accuracy, precision, f1-score, recall score, and auc score. 
\FloatBarrier
\begin{table}[H]
	\centering
	\begin{tabular}{| p{4cm} | c | c | c | c | c |}
		\hline
		Model & Accuracy & Precision & f1-score & recall & auc-score\\
		\hline
		Our Proposed & 0.9	& 0.86 &\textbf{0.86} & \textbf{0.81} & \textbf{0.99}\\
		\hline
		InceptionResNetV2\cite{03358} & 0.93 & 0.89 & 0.75 & 0.71 & \textbf{0.99}\\
		\hline
		\cite{03798} & - & 0.88 & 0.77 & 0.74 & - \\
		\hline
		\cite{09418} & 0.88 & - & - & - & - \\
		\hline
		\cite{01284} & 0.86 & - & - & - & - \\
		\hline
		GradCam and Kernel SHAP\cite{06612} & 0.88 & - & - & - & - \\
		\hline
		Student and Teacher\cite{03225} & 0.85 & 0.76 & 0.76 & - & - \\
		\hline
	\end{tabular}
	\caption{Comparative Analysis}
	\label{table:comparative-analysis}
\end{table}
